curiobaby_drop model analysis

### 2021-01-25 analysis/model_analysis_v2.Rmd
tried combinations of features

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism")) 
  #select(-`obj_final_position_std_objects=drop`, -`obj_final_position_std_objects=target`)
# these cols are all 0...

@@

@@

plot_model_preds <- function(feat_name, fits, hum_data, age="adults") {
  beta = subset(fits, AgeGroup==age & feature==feat_name)$beta
  md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
  md %>% ggplot(aes(x=chose_target, y=Model_targ_prop, color=relation)) +
    geom_abline(slope=1, intercept=0, linetype="dashed") +
    geom_point(alpha=.5) + 
    xlab("Human Choice Probability") + 
    ylab("Model Choice Probability") +
    ggtitle(paste0(feat_name,": ",age)) + theme_minimal() + 
    xlim(0,1) + ylim(0,1)
}

ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults")
ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children")

@@

```{r}
ad <- plot_model_preds("sharpness_of_support_posjitter_response", fits, adult_trial_agg, age="adults")
ch <- plot_model_preds("sharpness_of_support_posjitter_response", fits, child_trial_agg, age="children")

@@

```{r}
ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults")
ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children")

@@

```{r}
ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults")
ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children")

@@

>>>>

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism"))

colMeans(mdat[,1:22])
# obj_final_position_invstd_objects=drop = -0.2980893  should that be negative?

# engineer some features: 
# combine target + drop target features
mdat_eng <- mdat %>%
  mutate(obj_final_position_std = 
           `obj_final_position_std_objects=drop` + 
           `obj_final_position_std_objects=target`,
         normed_velocity_std_after_first_collision_objects = 
           `normed_velocity_std_after_first_collision_objects=drop` + 
           `normed_velocity_std_after_first_collision_objects=target`,
         avg_final_radius_objects = 
           `avg_final_radius_objects=drop` + 
           `avg_final_radius_objects=target`,
         avg_max_radius_objects = 
           `avg_max_radius_objects=drop` + 
           `avg_max_radius_objects=target`,
         max_radius_std_objects = 
           `max_radius_std_objects=drop` + 
           `max_radius_std_objects=target`,
         support_combo = 
           support_probability + 
           support_std + 
           `support_response_sharpness_C=1e-05`, # add one of support_response_linearity_r or _pv ?
         len_combo = avg_len + len_std + len_inverse_sharpe_ratio
         ) %>%
  select(-`obj_final_position_std_objects=drop`, 
         -`obj_final_position_std_objects=target`,
         -`normed_velocity_std_after_first_collision_objects=drop`,
         -`normed_velocity_std_after_first_collision_objects=target`,
         -`avg_final_radius_objects=drop`,
         -`avg_final_radius_objects=target`,
         -`avg_max_radius_objects=drop`,
         -`avg_max_radius_objects=target`,
         -`max_radius_std_objects=drop`,
         -`max_radius_std_objects=target`,
         -support_probability, 
         -support_std,
         -`support_response_sharpness_C=1`,
         -`support_response_sharpness_C=1e-05`,
         -`support_response_sharpness_C=100000.0`,
         -avg_len, -len_inverse_sharpe_ratio, -len_std,
         -support_response_linearity_pv, -support_response_linearity_r,
         -`obj_final_position_invstd_objects=target`,
         -`obj_final_position_invstd_objects=drop`
         )

@@

## Now try engineered features

```{r adult-eng-feats}
feat_names2 = names(mdat_eng)[5:ncol(mdat_eng)]

for(feat in feat_names2) {
  feat_df <- get_feature_df(mdat_eng, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=adult_trial_agg)
  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=child_trial_agg)
}

@@

plot_model_preds <- function(feat_name, fits, hum_data, age="adults", mdat) {
  beta = subset(fits, AgeGroup==age & feature==feat_name)$beta
  md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
  md %>% ggplot(aes(x=chose_target, y=Model_targ_prop, color=relation)) +
    geom_abline(slope=1, intercept=0, linetype="dashed") +
    geom_point(alpha=.5) + geom_smooth(method='lm') + 
    xlab("Human Choice Probability") + 
    ylab("Model Choice Probability") +
    ggtitle(paste0(feat_name,": ",age)) + theme_minimal() + 
    xlim(0,1) + ylim(0,1)
}

ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults", mdat)
ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children", mdat)

@@

```{r}
ad <- plot_model_preds("support_combo", fits, adult_trial_agg, age="adults", mdat_eng)
ch <- plot_model_preds("support_combo", fits, child_trial_agg, age="children", mdat_eng)

@@

```{r}
ad <- plot_model_preds("support_response_sharpness_C=1e-05", fits, adult_trial_agg, age="adults", mdat)
ch <- plot_model_preds("support_response_sharpness_C=1e-05", fits, child_trial_agg, age="children", mdat)

@@

```{r}
ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults", mdat)
ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children", mdat)

@@

```{r}
ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults", mdat)
ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children", mdat)
